Predicting detection probabilities for rare and undersampled North American landbirds

### 2023-10-25 article/article.tex
points of what to write next
added more posthoc analysis discussion to paper

\par Similar to multi-species removal modelling, estimates of EDR fell roughly where we would expect based on species of similar traits, for the species where we were relaxing samples sizes.

>>>>

\par Similar to multi-species removal modelling, estimates of EDR fell roughly where we would expect based on species of similar traits, for the species where we were relaxing samples sizes.
For example, Harris's Sparrow (n = 13) had an estimated mean EDR of 65.6 m, with a 95\% credible interval of [53.1, 82.5].
This range does fall below the mean EDR of 85.3 m for the other sparrows in NA-POPS, but Harris's Sparrow song pitch of approximately 3.8 Hz falls above the average song pitch of 3.0 Hz for the other sparrows in NA-POPS, which could contribute to the smaller EDR.
On the other hand, LeConte's Thrasher (n = 1) had an estimated EDR of 134.2 m, with a 95\% credible interval of [81.8, 230.5], which falls roughly in line with the mean EDR of 113.2 m of the six other thrashers in NA-POPS.

\subsection{Model Performance}

* removal modelling was always okay

* distance model struggled significantly

\subsection{Recommendations for Multi-species Predictions of Detectability}
